BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2014-12-15 Paper/BOAST.tex
plural (those)

For these reasons, a convolution library has been engineered with the help of
BOAST.  *The detailed API of the library will be described elsewhere*.  The
spirit is similar to BLAS-LAPACK API, where low-level operations are scheduled
and called from high-level operations.  Each of the building blocks of these
convolution library is optimally tuned by BOAST by choosing the sources
providing the optimal kernel for the chosen computing platform.  The sources of
these kernels are then collected and compiled to meet the API of the library.

>>>>

For these reasons, a convolution library has been engineered with the help of
BOAST.  \textbf{The detailed API of the library will be described elsewhere}.  The
spirit is similar to BLAS-LAPACK API, where low-level operations are scheduled
and called from high-level operations.  Each of the building blocks of these
convolution libraries is optimally tuned by BOAST by choosing the sources
providing the optimal kernel for the chosen computing platform.  The sources of
these kernels are then collected and compiled to meet the API of the library.
